{\TheTitle}\thanks{Submitted to the editors DATE. \funding{This work was funded by the Fog Research Institute under contract no.~FRI-454.}}

### 2017-10-10 ssc-0-0.tex
writing

% Declare title and authors, without \thanks
\newcommand{\TheTitle}{Stability of the semi-implicit formula for quantum dynamics} 
\newcommand{\TheAuthors}{Rodney E. S. Polkinghorne}

@@

The semi-implicit method \cite{jkp-132-312,jkp-93-144} is often used to solve stochastic partial differential equations that arise when Monte-Carlo methods are used in quantum optics and in atom optics \cite{pra-58-4824}.  This is done as a method of lines, in which the spatial axes are discretised, often by spectral derivatives, to give a system of ordinary differential equations.  The semi-implicit formula is then used to integrate these.

>>>>

% Declare title and authors, without \thanks
\newcommand{\TheTitle}{Stability of the iterative semi-implicit formula for quantum dynamics} 
\newcommand{\TheAuthors}{Rodney E. S. Polkinghorne}

@@

The semi-implicit formula is a rule for integrating systems of
ordinary differential equations \cite{jkp-132-312,jkp-93-144}.  It
is often used as a method of lines, to solve stochastic partial
differential equations that occur when phase space Monte-Carlo
methods are used in quantum optics and in atom optics \cite{pra-58-4824}.
This is done as a method of lines, in which the spatial axes are
discretised, often by spectral derivatives, to give a system of
ordinary differential equations \cite{2000-Trefethen-Spectral}.
The semi-implicit formula is then used to integrate these.

{\bf Relate Hilbert space expansions to methods of lines.}
